The Effects of Telluric Lines in Radial Velocity Searches for Planets with Iodine Cell as Calibrators\altaffilmark{1}

### 2015-07-31 ms.tex
Back up the master ms.tex which has skeleton for all work.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

I'll keep the first paragraph so there are some references -- also
because it's cool. Jupiter analogs orbiting other stars represent the first signposts of
true Solar System analogs, and the eccentricity distribution of these
planets with $a>3$ AU will reveal how rare or frequent true Jupiter
analogs are. To date, only 9 ``Jupiter analogs" have been
well-characterized in the peer reviewed literature\footnote{HD
  13931$b$ \citep{2010ApJ...721.1467H}, HD 72659$b$
  \citep{2011A&A...527A..63M}, 55 Cnc $d$ \citep{2002ApJ...581.1375M},
  HD 134987$c$ \citep{2010MNRAS.403.1703J}, HD 154345$b$ \citep[but
    with possibility of being an activity cycle-induced
    signal]{2008ApJ...683L..63W}, $\mu$ Ara $c$
  \citep{2007A&A...462..769P}, HD 183263$c$
  \citep{2009ApJ...693.1084W}, HD 187123$c$
  \citep{2009ApJ...693.1084W}, and GJ 832$b$
  \citep{2009ApJ...690..743B}.}  \citep[defined here as $P > 8$ years,
  $4 > M\sin{i} > 0.5\ \mjup$, and $e <
  0.3$;][exoplanets.org]{wrighteod}. As the duration of existing
planet searches approach 10--20 years, more and more Jupiter analogs
will emerge from their longest-observed targets
\citep{2012arXiv1205.2765W, 2012arXiv1205.5835B}.

%----------------------------------------------------------------
% SME Parameters Table
\renewcommand{\arraystretch}{1.2} % more row spacing for the table
\begin{deluxetable}{lc}
\tabletypesize{\scriptsize}
\tablecaption{STELLAR PARAMETERS\label{smetable}}
\tablewidth{180pt}
\tablehead{
  \colhead{Parameter} & \colhead{Value~~}
}
\startdata
~~Spectral type\tablenotemark{a} & K0 V ~~ \\
~~Distance (pc)\tablenotemark{a} & 44.0 $\pm$ 2.1 ~~ \\
~~$V$ & 8.661 $\pm$ 0.013 ~~ \\
%$B-V$           &   ~~ \\ % not seen B-V in Jeff's SME file
~~$T_{\mbox{eff}}$ (K) & 5448 $\pm $44 ~~ \\
~~$\log{g}$ & 4.511 $\pm$ 0.024 ~~ \\
~~$[$Fe/H$]$ & 0.336 $\pm$ 0.030 ~~ \\
%~~$v\sin{i}$ (k\mps) & 0.14 $\pm$ 0.5 ~~ \\ % no detection available
~~BC & -0.144 ~~ \\
~~$M_{\mbox{bol}}$ & 5.301 ~~ \\
~~$L_{\star}$ ($L_{\odot}$) & 0.590 $\pm$ 0.058 ~~ \\
~~$R_{\star}$ ($R_{\odot}$) & 0.901 $\pm$ 0.015 ~~ \\
~~$M_{\star}$ ($\msol$) & 1.000 $\pm$ 0.017 ~~ \\
~~$v\sin{i}$ & $<1$ k\mps ~~ \\
~~Age\tablenotemark{b}  & $\sim 7$ Gyr ~~
%S$_{HK}$         &   ~~ \\
%log$R'_{HK}$     &   ~~ \\
%$P_{rot}$ (days) &
\enddata
\tablenotetext{a}{\cite{esa1997,vanleeuwen2008}.}
\tablenotetext{b}{\cite{svalue2010}, see section.}
\end{deluxetable}
%----------------------------------------------------------------

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}\label{sec:intro}

We are going to cite \cite{artigau2014, cunha2014} and \cite{hitran2013}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Simulating Keck/HIRES Spectra}\label{sec:simulating}

Introduction to Keck/HIRES CPS data, data reduction, Doppler code. Our
adoption of Doppler code.

Introduction to the standard star(s) in this paper?

ZZZ Table: standard star stellar properties? esp. coordinates to
highlight BC ranges?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Injecting Telluric Lines}\label{sec:injecting}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Simulated Data}

This is where TERRASPEC got introduced.

ZZZ Plots:

- telluric line atlas in the optical? just to demonstrate where they are.

- telluric free simulations to demonstrate RV precision, vs. year,
vs. BC

- telluric injected simulations to demonstrate effects, vs. year, vs. BC

- RV vs. BC for chunks with and without telluric lines before and
after injection

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{On-Sky Data}

Should this be the first?

ZZZ Plots:

- RV vs. year/time, RV vs. BC

- RV from chunks with and without telluric lines, vs. BC

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Where and How Telluric Lines Enter the Data}

Should this subsection be moved to the first?
It enters the epoch data as well as the empirically derived stellar template.

ZZZ Plots:

- fitting plots showing data (with telluric highlighted) and DSST
(tellurics highlighted) and the mismatch

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Correcting for the Effects of Telluric Lines}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Masking out the Telluric Lines}

ZZZ Plot:

- Illustration of choice of mask

- RV vs. BC before and after for all, telluric, and non-telluric chunks

- simulation results showing no aliases introduced by masking

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Removing the Telluric Contamination from Stellar Templates}

ZZZ Plot:

- selected chunk before and after cleaning

- ?RV vs. BC using cleaned template, no masking, single mask?, double mask?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Modeling Telluric Lines in the Star$+$Iodine Spectra}

ZZZ Plot:

- RV vs. BC using cleaned template plus full telluric modeling

- RV vs. BC using cleaned template plus full modeling plus some masking?

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Results for A Different RV Standard Star}

I think this is a must! At least one more star, hopefully two.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Summary and Future Work}\label{sec:summary}

Gaussian processes!
